On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-04-09 docs/mvfits_paper/mvf.tex
clarifying 4th vs 5th order polynomials for QNM fitting

    {\includegraphics[width=0.49\textwidth]{fits_w.pdf}} & {\includegraphics[width=0.49\textwidth]{fits_tau.pdf}}

@@

    \hspace{0.35cm}\includegraphics[width=0.43\textwidth]{res_cw_0.pdf} & \hspace{0.3cm}\includegraphics[width=0.43\textwidth]{res_cw_1.pdf}

@@

>>>>

    {\includegraphics[width=0.49\textwidth,trim={0 0.2in 0 0.4in},clip]{fits_w.pdf}} & {\includegraphics[width=0.49\textwidth,trim={0 0.2in 0 0.4in},clip]{fits_tau.pdf}}

@@

    {\includegraphics[width=0.49\textwidth,trim={0 0.25in 0 0.9in},clip]{res_cw_0.pdf}} & {\includegraphics[width=0.49\textwidth,trim={0 0.25in 0 0.9in},clip]{res_cw_1.pdf}}

@@

For the zero-damped \qnm{s}, we note that 4th order polynomials were actually modeled, with the remaining power of $\kappa$ resulting from explicit enforcement of the zero-damped condition.
